Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-28 paper/ms.tex
Line length fix
Add neighborhood column to table

\begin{deluxetable*}{ccccccc}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within
$250\,\pc$ of the Sun.\label{tab:real_clusters}}
\tablehead{\colhead{cluster} & \colhead{distance} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} \\ \colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$}}f
\startdata
alphaPer & 174.9 & 14.0 & -1739 & 0.0045 & 10.5 & 352\tablenotemark{b} \\
Blanco1 & 237.2 & 1.6 & -1841 & 1.53 & 207.0 & 410\tablenotemark{c} \\
ComaBer & 85.9 & 1.6 & -1860 & 0.71 & 139.7 & 112\tablenotemark{d} \\
Hyades & 47.5 & 20.3 & -1757 & 0.26 & 81.5 & 400\tablenotemark{e} \\
IC2391 & 151.6 & 5.5 & -1790 & 0.018 & 21.2 &  \\
IC2602 & 152.2 & 11.5 & -1718 & 0.32 & 88.6 & \\
NGC2451A\tablenotemark{a} & 193.7 & 5.8 & -1805 & 0.21 & 73.4 & \\
Pleiades & 135.8 & 19.3 & -1696 & 0.38 & 96.3 & \\
Praesepe & 186.2 & 21.2 & -1766 & 0.58 & 122.9 & 550\tablenotemark{d}
\enddata

>>>>

\begin{deluxetable*}{cccccccc}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within
$250\,\pc$ of the Sun.\label{tab:real_clusters}}
\tablehead{\colhead{cluster} & \colhead{distance} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} & \colhead{neighborhood} \\ 
\colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$} & \colhead{$\mathrm{pc}$}}
\startdata
alphaPer & 174.9 & 14.0 & -1739 & 0.0045 & 10.5 & 352\tablenotemark{b} & 57 \\
Blanco1 & 237.2 & 1.6 & -1841 & 1.53 & 207.0 & 410\tablenotemark{c} & 1460 \\
ComaBer & 85.9 & 1.6 & -1860 & 0.71 & 139.7 & 112\tablenotemark{d} & 522\\
Hyades & 47.5 & 20.3 & -1757 & 0.26 & 81.5 & 400\tablenotemark{e} & 462 \\
IC2391 & 151.6 & 5.5 & -1790 & 0.018 & 21.2 & & \\
IC2602 & 152.2 & 11.5 & -1718 & 0.32 & 88.6 & & \\
NGC2451A\tablenotemark{a} & 193.7 & 5.8 & -1805 & 0.21 & 73.4 & & \\
Pleiades & 135.8 & 19.3 & -1696 & 0.38 & 96.3 & & \\
Praesepe & 186.2 & 21.2 & -1766 & 0.58 & 122.9 & 550\tablenotemark{d} & 781
\enddata
